The Socialization of Meritocracy: The role of the Family and the School

### 2023-06-07 abstract_effor23.Rmd
ajustes conferencia

# Renderizar tabla
knitreg(list(getah.or0.1,getah.or0.2,getah.or0.3,
             # getah.or1,
             getah.or6,
             # getah.or7,
             getah.or8),
        caption = paste("(\\#tab:getah)",cap1),
        caption.above=TRUE,
        omit.coef=omit_coef,
        include.thresholds=FALSE,
        custom.gof.rows=list(Controls=c("No","No","No",
                                        # "No",
                                        # "Yes",
                                        "Yes","Yes")),
        groups=list("Sense of Justice in grades - Direct (ref: The ones I deserve)"=2:3,
                    "Parental Perc. Meritocracy (ref: Not important)"=4,
                    "Household income (ref: Quintile 1)"=5:9,
                    "Interaction: Parental Perc. Meritocracy x SJ in grades - Direct" = 12:13),
        custom.coef.names=coef_names,
        scalebox = 0.75,
        threeparttable = T,
        custom.note="\\item *** p < 0.001; ** p < 0.01; * p < 0.05; \\item ¹Note: the perception of parent’s meritocracy was collapsed into dummies, where the category 'It is important' (1) includes the categories 'Very important', 'Important' and 'Somewhat important' and the reference category 'Not important' (0) corresponds to the category 'Not at all important'."
        #file = "output/tables/trabajoduro_ppt.html"
        )
#webshot::webshot("output/tables/trabajoduro_ppt.html","output/tables/trabajoduro_ppt.png")
```

>>>>

# Renderizar tabla
htmlreg(list(getah.or0.1,getah.or0.2,getah.or0.3,
             # getah.or1,
             getah.or6,
             # getah.or7,
             getah.or8),
        caption = paste("(\\#tab:getah)",cap1),
        caption.above=TRUE,
        omit.coef=omit_coef,
        include.thresholds=FALSE,
        custom.gof.rows=list(Controls=c("No","No","No",
                                        # "No",
                                        # "Yes",
                                        "Yes","Yes")),
        groups=list("Sense of Justice in grades - Direct (ref: The ones I deserve)"=2:3,
                    "Parental Perc. Meritocracy (ref: Not important)"=4,
                    "Household income (ref: Quintile 1)"=5:9,
                    "Interaction: Parental Perc. Meritocracy x SJ in grades - Direct" = 12:13),
        custom.coef.names=coef_names,
        scalebox = 0.75,
        threeparttable = T,
        custom.note="\\item *** p < 0.001; ** p < 0.01; * p < 0.05; \\item ¹Note: the perception of parent’s meritocracy was collapsed into dummies, where the category 'It is important' (1) includes the categories 'Very important', 'Important' and 'Somewhat important' and the reference category 'Not important' (0) corresponds to the category 'Not at all important'.",
        file = "output/tables/trabajoduro_ppt.xls"
        )
#webshot::webshot("output/tables/trabajoduro_ppt.html","output/tables/trabajoduro_ppt.png")
```
